Structuring College Access

### 2025-03-03 index.qmd
tweaking presentation and AI/AN slides

# 1) Define the `insert_figure` helper function
insert_figure <- function(rq, metro, graph_type, base_path = graphs_dir) {

  # We'll use 'metro' directly since it's already underscored (e.g. "los_angeles").
  fig_file  <- file.path(base_path, rq, str_c(rq, "_", metro, "_", graph_type, ".png"))
  cap_file  <- file.path(base_path, rq, str_c(rq, "_", metro, "_", graph_type, "_title.txt"))
  note_file <- file.path(base_path, rq, str_c(rq, "_", metro, "_", graph_type, "_note.txt"))

  # Print a heading / caption
  caption_text <- if (file.exists(cap_file)) readLines(cap_file, warn = FALSE) else "No Title Found"
  writeLines(paste0("#### ", caption_text))

  # Output the figure (if it exists)
  if (file.exists(fig_file)) {
    writeLines(str_c("![](", fig_file, ")\n"))
  } else {
    writeLines(paste("*(Missing figure file:", fig_file, ")*\n"))
  }

  # Print footnotes (if the .txt file exists)
  if (file.exists(note_file)) {
    notes_txt <- readLines(note_file, warn = FALSE)
    writeLines(
      str_c(
        "<div class=\"footnote\">",
        paste0(notes_txt, collapse = "</br>"),
        "</div>"
      )
    )
  }
}

@@

@@

@@

writeLines("## AI/AN students")

@@

  # Determine the heading text for each metro:
  # If m == 'nyny', use "New York City".
  # Otherwise, convert underscores -> spaces, then "Title Case + area".
  heading_text <- if (m == "nyny") {
    "New York City"
  } else {
    # Normal logic
    metro_no_underscores <- gsub("_", " ", m, fixed = TRUE)
    title_case           <- tools::toTitleCase(metro_no_underscores)
    paste0(title_case, " area")
  }

  # For each metro, we produce 3 slides
  for (i in seq_along(var_rc_pairs)) {

    # If this is the 1st slide => show in TOC (no .hide).
    # Otherwise => hide from TOC with {.hide}.
    if (i == 1) {
      writeLines(str_c("### ", heading_text))
    } else {
      writeLines(str_c("### ", heading_text, " {.hide}"))
    }

    # Extract the variable (firstgen/race) and approach (row/col)
    g  <- var_rc_pairs[[i]][1]
    rc <- var_rc_pairs[[i]][2]

    # Build the figure name: e.g. "race_row_plot_487927"
    graph_type_native <- str_c(g, "_", rc, "_plot_", native_order)

    # Call your helper function; it prints "#### <title from _title.txt>"
    # and displays the figure + footnotes.
    insert_figure(
      rq         = "rq2",
      metro      = m,
      graph_type = graph_type_native
    )
  }
}

```

>>>>

# Revised insert_figure() that does NOT print a heading
insert_figure <- function(rq, metro, graph_type, base_path = graphs_dir) {

  # We'll use 'metro' directly since it's already underscored (e.g. "los_angeles").
  fig_file  <- file.path(base_path, rq, stringr::str_c(rq, "_", metro, "_", graph_type, ".png"))
  cap_file  <- file.path(base_path, rq, stringr::str_c(rq, "_", metro, "_", graph_type, "_title.txt"))
  note_file <- file.path(base_path, rq, stringr::str_c(rq, "_", metro, "_", graph_type, "_note.txt"))

  # Print a heading/caption
  caption_text <- if (file.exists(cap_file)) readLines(cap_file, warn = FALSE) else "No Title Found"
  writeLines(paste0("#### ", caption_text))

  # Output the figure (if it exists)
  if (file.exists(fig_file)) {
    writeLines(stringr::str_c("![](", fig_file, ")\n"))
  } else {
    writeLines(paste("*(Missing figure file:", fig_file, ")*\n"))
  }

  # Print footnotes (if the .txt file exists)
  if (file.exists(note_file)) {
    notes_txt <- readLines(note_file, warn = FALSE)
    writeLines(
      stringr::str_c(
        "<div class=\"footnote\">",
        paste0(notes_txt, collapse = "</br>"),
        "</div>"
      )
    )
  }
}

@@

      # -- HERE is the new line to remove "487927" --
      orders_for_m <- orders_for_m[ orders_for_m != "487927" ]

@@

# A special version insert_figure_aian for AI/AN that does NOT print a heading
insert_figure_aian <- function(rq, metro, graph_type, base_path = graphs_dir) {

  fig_file  <- file.path(base_path, rq, paste0(rq, "_", metro, "_", graph_type, ".png"))
  cap_file  <- file.path(base_path, rq, paste0(rq, "_", metro, "_", graph_type, "_title.txt"))
  note_file <- file.path(base_path, rq, paste0(rq, "_", metro, "_", graph_type, "_note.txt"))

  # Instead of printing a heading, let the AI/AN loop do it (#### subtitle).
  # So we skip caption_text or print it differently if you want.

  if (file.exists(fig_file)) {
    writeLines(paste0("![](", fig_file, ")\n"))
  } else {
    writeLines(paste("*(Missing figure file:", fig_file, ")*\n"))
  }

  # Print footnotes (if the .txt file exists)
  if (file.exists(note_file)) {
    notes_txt <- readLines(note_file, warn = FALSE)
    writeLines(
      paste0(
        "<div class=\"footnote\">",
        paste0(notes_txt, collapse = "</br>"),
        "</div>"
      )
    )
  }
}

@@

# (Level-1) "AI/AN students"
writeLines("# AI/AN students\n")

@@

  # (Level-2) heading for each metro (not a slide at slide-level=3)
  heading_text <- if (m == "nyny") {
    "New York City"
  } else {
    m_no_underscores <- gsub("_", " ", m, fixed = TRUE)
    m_title          <- tools::toTitleCase(m_no_underscores)
    paste0(m_title, " area")
  }
  writeLines(paste0("## ", heading_text, "\n"))

  # For each var/rc pair, create a new slide at level-3 (always hidden in TOC)
  for (i in seq_along(var_rc_pairs)) {

    g  <- var_rc_pairs[[i]][1]
    rc <- var_rc_pairs[[i]][2]

    # Always hidden from TOC => add "{.hide}" every time
    writeLines(paste0("### ", heading_text, " (AI/AN) {.hide}\n"))

    # (Level-4) subtitle on the same slide
    subtitle <- if (g == "firstgen") {
      "First-generation status composition of purchased AI/AN student profiles by geomarket"
    } else if (g == "race") {
      "Racial composition of purchased AI/AN student profiles by geomarket"
    } else {
      "Other composition of purchased AI/AN student profiles"
    }
    writeLines(paste0("#### ", subtitle, "\n"))

    # Build figure name and call your "no-heading" figure function
    graph_type <- paste0(g, "_", rc, "_plot_", native_order)
    insert_figure_aian(
      rq         = "rq2",
      metro      = m,
      graph_type = graph_type
    )
  }
}
```
